### 2025-01-03 paper/main.tex
updated paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{LoRA}
Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2021lora}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{LoRA}
Among the different techniques for parameter-efficient fine-tuning of LLMs, one of the most relevant approaches of the last years has been LoRA (Low-Rank Adaptation of Large Language Models) \cite{hu2022lora}. The idea behind LoRA is
